Regime transition identification for water utilization of river basin

### 2020-10-24 tex/main/manuscript.tex
fixed by wu's suggestions

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for water utilization in river basin developments}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
\author[a, b]{Bojie Fu}  % 傅老师
\author[c, d]{Xutong Wu}  % 武旭同

@@

%tag 摘要
\begin{abstract}
	For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
	Here, considering three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, our results suggest there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework of relationships associated regime shifts with developments.
	By predicting widespread development dilemmas in transition regimes of water utilization, it can be a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

@@

% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects. 
% TODO 这里增加三篇“大文章”参引
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% TODO 这里增加参考文献，人类对水循环的改造 
% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}. 
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
Therefore, understanding the complex relationship between human societies, water resources utilization and their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.

% tag 引言第二段
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is supplying for human societies in further developments based on water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt drivers triggered regime shifts as societies' development strengthen their interlinks to water utilization and deepening dependences on them.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.

@@

% Tag 引言第三段
% 前人已经从不同维度刻画了人水关系.
Features of water utilization has been depicted and studied from various intertwined perspectives so far.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, water stresses are of increasing importance and concerns because of scarcity.
Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the need of developments, priority of water utilization changed with and there are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
% 全球总的取水量很少，但缺水地区很多
As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
% 将三种视角结合，就是“水资源利用体系”。
As these dimensions haven't been well integrated by quantitative methods, however, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} two change points in 1978 and 1994, three periods were detected in changing trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}

% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods} and \textit{SI Appendix} Methods S4) (Figure~\ref{fig:IWRU}).
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (83.7\%), while priority and configuration of the water utilization had slight negative contribution (5.6\% and 10.7\%).
% 第二阶段
In the second period (P2, 1979-1994), though increased positive contributions of priority and configuration (27.8\% and 22.0\% respectively), the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (50.2\% contribution but in negative). 
% 第三阶段
However, as the further increasing of positive contributions of priority (36.1\%) and configuration (38.3\%), and decreases of water stresses in negative contribution (25.6\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress (83.7\%); P2 is priority (27.8\%); and P3 is configuration (38.3\%).

% 三个维度（压力、优先性、配置）的在每年也有各自的变化趋势，将三者结合后，呈现出阶段特征明显
While the above three dimensions (stress, priority and configuration) also have own variation (see \textit{SI Appendix} Methods S4 and Fig. S4), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C). When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses. After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

Some main drivers caused the above changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
(2) During the P3, irrigation had noticeable changes in its efficiency, whose water consumptions were reduced but still dominant. Although irrigated area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes}A and Figure~\ref{fig:Causes}B). It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
(3) Changing water management practice contributed throughout all three periods. In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).

@@

\subsection*{Shifted water utilization regimes with development}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S9). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. In 1972, the Yellow River was dried up for the first time with a length of 310 km for 19 days, and continued to be dried up for many years since then (\textit{SI Appendix} Fig. S10). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
The next regime shift was not occurred by a significant increase in water use efficiency in about 1993. 
% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig. S9).
% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture. As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig. S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).

In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system. Since they have driven the YRB to change regimes twice between 1965 and 2013 along with social development, it can be interpreted as a transition process towards comprehensive water utilization.

@@

	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
	We believe that water resources utilization system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):

@@

	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWRU)，使 IWRU 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension after which, the above equation is transformed into a natural logarithm to facilitate calculation:

>>>>

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for water utilization of river basin}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[a, b]{Bojie Fu}  % 傅老师

@@

%tag 摘要
\begin{abstract}
	\label{abstract}
	% For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
	Detecting these abrupt reorganizations of structure and function is crucial for understanding changes of human-water system. 
	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, it suggests that there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework in interpreting associated changes.
	By identifying and predicting widespread dilemmas in transition of water utilization, this framework can be a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

@@

\label{introduction}
% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects. 
% TODO 这里增加三篇“大文章”参引
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
However, human's modification has profoundly influenced the water cycle, which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% TODO 这里增加参考文献，人类对水循环的改造 
% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, urgently need integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}. 
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
Since it requires deep understanding of the complex relationships between human societies and water resources utilization, sketching their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.

% tag 引言第二段
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is sustaining the development of human societies through water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, such as water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt changes triggered regime shifts as societies' development strengthen their interlinks to water utilization with increased dependences.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.

@@

% Tag 引言第三段
% 前人已经从不同维度刻画了人水关系.
Features of water utilization has been depicted and studied from various intertwined perspectives.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, water stresses are of increasing importance and concerns.
Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the priority of water utilization changed with the need of development. 
There are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
% 全球总的取水量很少，但缺水地区很多
% As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
% \cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
% 将三种视角结合，就是“水资源利用体系”。
However, these dimensions haven't been well integrated by quantitative methods, and a coherent interpret of regime shifts regard to social development and water utilization is needed.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} Change points detection. With change points in 1978 and 1994, the IWRU have three periods in changing trend.
	\textbf{B,} Changing slopes of each period.
	\textbf{C,} Contributions of each dimension to the changes of IWRU within three periods. Stress, priority and configuration are the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWRU}
\end{figure}

% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points, the changing trend of IWRU index are detected into three periods (Figure~\ref{fig:IWRU}A). 
Not only the slope of changes are various within each period, changes are also mainly contributed by different dimensions (Figure~\ref{fig:IWRU}B and Figure~\ref{fig:IWRU}C).
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (131\%), while priority and configuration of the water utilization had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of priority and configuration turned into positive, the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of priority (75\%) and configuration (84\%), and decreases of water stresses in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C). When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}

% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
Taken together, each period has the unique most striking positive contributor to IWRU, and overall features of three dimensions in different periods are shown in Figure~\ref{fig:phases}.
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses. After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

Various main drivers caused the above changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
Firstly, the expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
Secondly, efficiency of water utilization changed from the P2 to the P3.
While irrigated area resumed expansion again in the P3 whose water consumptions were still dominant (Figure\ref{fig:Causes}A), both industry, urban services were boosting their gross added values (GVA) (Figure~\ref{fig:Causes}B). 
However, the water use density (WUI) of them experienced significant declines and reached the lowest points (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
Finally, changing water management practice contributed throughout all three periods. 
According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
In the P1, most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).

@@

\subsection*{Shifted water utilization regimes with the development of society}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures the complex human-water feedbacks that links social development and water resources utilization from three dimensions (stress, priority and configuration). 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
At the beginning of P1, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S9). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure \cite{yellowriverarchivesOrganizationalHistoryYellow2004}, and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. As the most obvious performance, the Yellow River was dried up for several times since 1972 (\textit{SI Appendix} Fig. S10). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
During the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been constrained (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the Reform and Opening-up policy. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
The next regime shift was not occurred until a significant increase in water use efficiency since about 1993. 
% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig. S9).
% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture. As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig. S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).

In short, agricultural expansion, industries and services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system. They have driven the YRB to change regimes twice between 1965 and 2013, which can be interpreted as a transition process along with social development.

@@

	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
	% 我们认为水资源利用制度，与水资源利用的三个维度紧密相关：
	Water resources utilization system is closely related to the social developments in three dimensions below (see \textit{SI Appendix} Methods S4 for details):

@@

	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources Utilization, IWRU)，使 IWRU 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, C or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
	To effectively represent the three dimensions, we select an appropriate indicator ($I_x$, $x=P$, $C$ or $S$ corresponding to Priority, Configuration and Stress respectively) for each dimension. Then, the above equation is transformed into a natural logarithm to facilitate calculation:
